---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Find Percentage of Rating of Car Regarding Safety 

## 1.0 Introduction

I found the data sources from:

- https://www.kaggle.com/elikplim/car-evaluation-data-set

- https://data.world/uci/car-evaluation

I address two in my analysis:

- Does there exist a high percentage of cars that cost high, medium and low values that rate as high, medium regarding safety?
- Considering only high, medium and low 'buying price' of cars, what percentage of 2, 3, 4 seat cars rate high, medium and low concerning safety?

## 2.0 Synopsis

I:

1. Loaded the csv file.
2. Found the percentage of cars safety that rate as high, low and med for each buying price category (v.high, high, med, low).
3. Found the percentage of cars safety that rate as high, low and med for two, three and four seater cars.
4. Produced multi panels of a graph using ggplot2.
5. Produced a panel for each buying category.  Each panel contains a bar chart of percentage of cars that rate as high, low and med.
6. Filtered only rows of buying price of high, medium and low values.
7. Produced a second multi-panel of a graph using ggplot.
8. Took the filtered rows and produced a panel for each car seat category of two, three or four.  Each subplot contains a bar chart of percentage of cars that rate as high, low and med.


```{r Load}
#step 1 - create the working directory

setwd("C:/Users/Elias/Desktop/cars/cars")

file_car<- read.csv("car_evaluation.csv", header = FALSE, col.names = c('buying.price', 'maintaince.cost', 'number.doors', 'number.persons', 'lug.boot', 'safety', 'decision'))

file_car[1:10]
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
